---
title: "AE 05"
subtitle: "NC Bike Crashes"
date: "Due: September 2, 11:59PM"
author: "YOUR NAME GOES HERE"
output: 
  html_document
---

## Clone a repo + start a new project

- Click on the link provided in the slides to create your own private repo for 
this exercise.

- If you need further instructions, refer back to Lab 01 linked
[here](https://www2.stat.duke.edu/courses/Fall20/sta199.001/labs/lab-01-post.html)

- Configure git by typing the following in the Console (using your GitHub
username and e-mail as appropriate)

```{r eval=FALSE}
library(usethis)
use_git_config(user.name="your name", user.email="your email")
```

## Practice with data wrangling

```{r load-packages, warning = FALSE, message = FALSE}
library(tidyverse)
```

The data set contains all North Carolina bike crash data from 2007-2014. The 
dataset was originally downloaded on September 6, 2018 and is available in the 
dsbox R package. 

Use the code below to load the data from the .csv file

```{r load-data, warning = FALSE, message = FALSE}
ncbikecrash <- read_csv("data/ncbikecrash.csv")
```

### Part 1

Display the first 10 rows of the ncbikecrash data set.

```{r}

```


### Part 2 

Filter for bike crashes in Durham County where the driver age group is 0 to 19.

```{r}

```

### Part 3

On which day of the week did the most bike crashes occur? Use the `count` 
function to get the number of bike crashes for each day (`crash_day`). Display 
the results in descending order.

```{r}

```

### Part 4

Calculate the average estimated driver speed (`driver_est_speed`) based on 
whether the crash was a hit and run (`hit_run`).

```{r}

```